Distance-bounding, privacy-preserving attribute-based credentials

### 2020-07-02 slides/contents.tex
Points out proven in DFKO and Tamarin, highlights speaker
Shortens one section title

\section{Distance-bounding proofs-of-knowledge}

@@

      \item Two versions:
        \begin{enumerate}
          \item Mutual trust
          \item \acs{PKI} based
        \end{enumerate}
    \end{itemize}
  \end{solution}
\end{frame}

\begin{frame}
  \begin{example}[Use cases]
    \begin{itemize}
      \item Distance bounding Direct Anonymous Attestation (TPM standard).
      \item Distance bounding, privacy-preserving attribute-based credentials 
        (CL04 \etc).
      \item BankID to enter the pub or buy from Systembolaget?
    \end{itemize}
  \end{example}
\end{frame}
}

@@

\mode<presentation>{%
  \begin{frame}
    \begin{question}
      \begin{itemize}
        \item How costly is this compared to non-\acs{DB} Schnorr?
      \end{itemize}
    \end{question}
  \end{frame}
}

We will now review the performance of the proposed protocols.
Since the construction is designed as a drop-in replacement for the Schnorr 
identification-scheme~\cite{Schnorr} as \iac{ZKPK} protocol, we will focus on 
how much we must \enquote{pay} for the \ac{DB} property.
We summarize the results in \cref{performance-overview}.

\begin{frame}
  \begin{table}
    \caption{%
      A summary of how costly \acl*{DB} is in terms of performance.
      The \acs*{PKI} version additionally needs one signature verification.
      \(m, l\in \mathcal{O}(\log \lambda)\).
    }\label{performance-overview}
    \begin{tabular}{lrrrr}
      \toprule
      Protocol
      & Rand.
      & Arith.
      & Exp.
      & Pairings\\
      \midrule
      Schnorr             & \(l\)             & 3    & 3      & 0\\
      DB, mutual          & \(ml\)            & 3m   & 3      & 0\\
      DB, \acs*{PKI} \(\sum\)
                          & \(8\lambda + ml\)
                          & \(10m+8\)
                          & \(25\)
                          & \(14\)\\
      ---\acs*{DHKE}      & \(\lambda\)       & 0    & 4      & 0\\
      ---CL04 blind       & \(2\lambda\)      & 0    & 5      & 8\\
      ---DB               & \(5\lambda + ml\)    & \(10m + 2\) & 6 & 0\\
      ---Verification     & 0    & 6 & 10 & 6\\
      \bottomrule
    \end{tabular}
  \end{table}
\end{frame}

\paragraph*{Mutual trust}

We start with the mutual-trust version of the protocol in \cref{DB-Schnorr-UWB} 
(see \cref{DB-Schnorr-UWB-figure}).

In \emph{one round} of the protocol, the cost of the verifier is that of 
generating \(m\) number of \(l\)-bit strings, instead of only one.
This costs the verifier a factor \(m\) of randomness.
The cost of the prover is that of computing \(m\) number of replies (\(s\gets 
\rho - c \alpha \mod q\)), instead of only one.

To achieve security, the protocol must be repeated \(n\) times.
We have the \(l\)-parameter which controls the soundness of the \ac{ZKPK} and 
the \(m\)-parameter controls the soundness of the \acl{DB}.
If we want to achieve 80 bits of security, we can let \(l = m = 6\) (remember, 
\(l\) must be logarithmic in the security parameter) and \(n = 14\).
This makes \acl{DB} a factor \(6\) more expensive over the 
\emph{malicious-verifier secure} Schnorr protocol.

\paragraph*{\acs*{PKI}}

The \ac{PKI} version of the protocol (\cref{DB-Schnorr-PKI,DBSHW-overview}) 
performs one signature verification and four additional proofs in parallel.
The cost for the verifier is one signature verification in addition to the 
factor \(m\) of randomness used.
On the prover side, we have the computations for the signature verification and 
four additional proofs in parallel, this changes the cost to a factor of \(5m\) 
for the prover: the prover must compute \(s_i = \rho - c_j \alpha_i\) for 
\(i\in \{1, \dotsc, 5\}, j\in \{1, \dotsc, m\}\).

The cost of the signature is the same as for Anon-Pass~\cite{AnonPass}, which 
implements a public transport pass using this signature scheme.
The signature need not be reverified \(n\) times, it is sufficient to verify 
that once and reuse the same blinding for all \(n\) repetitions of the 
protocol.
Thus it is only the \acl{PK} that must be rerun \(n\) times.

\paragraph*{Bit-by-bit}

The traditional bit-by-bit version of the protocol 
(\cref{DB-Schnorr-nbit,DB-Schnorr-nbit-figure}) is not as efficient.
That is due to \(m = 2\) being fixed in this case (there are only two responses 
to choose from), and consequently, we must have a larger value for \(n\) to 
achieve the desired security.

>>>>

\section[\acs*{DB} \acsp*{ZKPK}]{Distance-bounding \aclp*{ZKPK}}

@@

      \item Two versions:
        \begin{enumerate}
          \item Mutual trust
          \item \acs{PKI} based
        \end{enumerate}

      \item Proven in the DFKO model and Tamarin.
    \end{itemize}
  \end{solution}
\end{frame}

\begin{frame}
  \begin{example}[Use cases]
    \begin{itemize}
      \item Distance bounding Direct Anonymous Attestation (TPM standard).
      \item Distance bounding, privacy-preserving attribute-based credentials 
        (CL04 \etc).
    \end{itemize}
  \end{example}
\end{frame}
}

@@

\input{../performance.tex}
